---
title: "commoncalcs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{commoncalcs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(commoncalcs)
```
Routine data analysis may involve a series of common calculations (commoncalcs, geddit?) that (to my knowledge), lack existing R packages written with them in mind. These include calculating percentage growth over differing periods of time, or calculating weighted means.

`commoncalcs` aims to resolve these problems. It provides functions that can streamline code required to run such calculations, assuming you can provide some data in the right format and specify some key variables.

# Installation
You can install the package using RStudio's tool, or via the following code, using the listed file location.
```{r, eval = F}
devtools::install_github("shanej90/commoncalcs")
```

# Usage
`commoncalcs` currently provides three routine functions:
*`calc_percent_growth()`, which enables you to calculate either absolute or averaged per period growth over a user-defined number of periods.
*`calc_weighted_means()`, which will produce a weighted mean for variable groupings of your choice.
*`profile_over_time()`, which will profile numbers over a specified period of time. The most obvious use case of this is to spread the entire value of a contract over the contract's duration.
